Invasive chameleons released from predation display more conspicuous colors

### 2021-12-06 ms.Rmd
Added inetarction models

##########
# Chromatic Contrast - dS
##########
    # Fit the interaction  model
      DispBgrdCC_s6 <- lmer(dS ~ sc_svl + Population*Background_pop  + (1|ID), data=DisplayBgrd)
      summary(DispBgrdCC_s6)

    # Interaction test. Does the difference between Hawaii and Kenya depend on the background. It shouldn't. Wald F-test
      F_CC_Disp_pop_bgk <- Wald_test(DispBgrdCC_s6, constraints = constrain_zero(5), 
                                  cluster = DisplayBgrd$ID, vcov = "CR2")

@@

  # Reparameterise the interaction model to generate the contrasts. It's not surprising that there is no interaction because we are literatlly just shifting the environment. 
      CourtshipCC_s6 <- lmer(dS ~ sc_svl  + relevel(pop_background, ref = "Hawaii.Kenya")  + (1|ID), data=CourtshipBgrd)
      summary(CourtshipCC_s6)
  # Robust variance esatimation to correct SE's for fixed effects given spectral curves are used multiple times for generating JNDs for each individuals data. 
  robust_CourtshipCC_s6 <- clubSandwich::conf_int(CourtshipCC_s6, cluster = CourtshipBgrd$ID, vcov =  "CR2")

>>>>

##########
# Chromatic Contrast - dS
##########
    # Fit the interaction  model
      DispBgrdCC_s6 <- lmer(dS ~ sc_svl + Population*Background_pop  + (1|ID), data=DisplayBgrd)
      summary(DispBgrdCC_s6)
    clubSandwich::conf_int(DispBgrdCC_s6, cluster = DisplayBgrd$ID, vcov =  "CR2")
    # Interaction test. Does the difference between Hawaii and Kenya depend on the background. It shouldn't. Wald F-test. Although, somthing might be up with this one - effect size tiny but goes from non-sig to signficant. 
      F_CC_Disp_pop_bgk <- Wald_test(DispBgrdCC_s6, constraints = constrain_zero(5), 
                                  cluster = DisplayBgrd$ID, vcov = "CR2")

@@

  # Reparameterise the interaction model to generate the contrasts. It's not surprising that there is no interaction because we are literatlly just shifting the environment. 
      CourtshipCC_s6 <- lmer(dS ~ sc_svl  + relevel(pop_background, ref = "Hawaii.Kenya")  + (1|ID), data=CourtshipBgrd)
      summary(CourtshipCC_s6)

  # Robust variance esatimation to correct SE's for fixed effects given spectral curves are used multiple times for generating JNDs for each individuals data. 
  robust_CourtshipCC_s6 <- clubSandwich::conf_int(CourtshipCC_s6, cluster = CourtshipBgrd$ID, vcov =  "CR2")
